\documentclass[a4paper, 11pt]{article}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage[pdftex]{hyperref}

% Lengths and indenting
\setlength{\textwidth}{16.5cm}
\setlength{\marginparwidth}{1.5cm}
\setlength{\parindent}{0cm}
\setlength{\parskip}{0.15cm}
\setlength{\textheight}{22cm}
\setlength{\oddsidemargin}{0cm}
\setlength{\evensidemargin}{\oddsidemargin}
\setlength{\topmargin}{0cm}
\setlength{\headheight}{0cm}
\setlength{\headsep}{0cm}

\renewcommand{\familydefault}{\sfdefault}

\title{Data Mining: Learning from Large Data Sets - Fall Semester 2015}
\author{jo@student.ethz.ch\\ umarco@student.ethz.ch\\ meiled@student.ethz.ch\\}
\date{\today}

\begin{document}
\maketitle

\section*{Extracting Representative Elements}

Marco started out by implementing the k-means algorithm by hand, not leading to any satisfying results.

Jonathan's attempt was to use the K-Means clustering implementation from sklearn module as follows: In the first step a set of mappers create a set of cluster centers each. In the second part, all these cluster centers are reduced to the 100 cluster centers asked for in the project description. In our test environment we used 8 mappers (getting 12500 records each) and one reducer.

After some success with this method we changed to MiniBatchKMeans. This speeded up the computation, and even led to better results. We can not explain the latter.

The final issue was now to fine-tune the parameters such as size of mini-batches, and the number of clusters for the mapper and reducer. Therefore Jonathan implemented a parameter search script. It turned out that batch sizes of 700 and 700 clusters for the mapper (and of course 100 clusters for the reducer) optimized our score.

It's noteworthy that our final submission has a very high variance. The exactly same code led to our final score  of 8.60131 in the best case (submission 3722), but only to 13.17762 (sumbission 3791) in the worst case.

Daniel checked the lecture slides as well as the the web without finding any room for improvement and wrote the report.

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
